Lens Modeling in \sw

### 2014-06-29 text/partA.tex

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.8\linewidth]
             {fig/007025_kappa_encl}}
  \subfigure{\includegraphics[width=0.8\linewidth]
             {fig/007022_kappa_encl}}
  \subfigure{\includegraphics[width=0.8\linewidth]
             {fig/007021_kappa_encl}} \\
  \caption{Enclosed mass \kenc from three models of the same system.
    The upper panel corresponds to the model shown in \figref{7025},
    with the image-parities incorrect by a quarter-turn.  The middle
    corresponds to \figref{7022}, where the image parities were
    correct.  The lower panel corresponds to another model, where the
    image parities were incorrect by a half-turn.}
\label{fig:kapenc_compare_faulty}
\end{figure}

Figure \ref{fig:kapenc_compare_faulty} shows a comparison of input and
recovered mass profiles.  The panel shows a average $\kappa$ within a
given radius, as a function of radius.  The red curve is the true
value, and where it crosses unity (dotted horizontal line) is the
notional Einstein radius $\Theta_{\text{E, sim}}$.  The two blue
curves are the minimal and maximal mean enclosed $\kappa$ from the
internal ensemble in \spl.  The region between the blue curves is
shaded between the radii of the innermost and the outermost images ---
this is the confidence region from the modeling.  As we see, the
shaded blue is slightly above the red curve.  The Einstein Radius
$\Theta_\text{E}$ of the model is estimated crossing the mean enclosed
$\kappa$ (not plotted) with unity.

The panel shows a average $\kappa$ within a given radius, as a
function of radius.  The red curve is the true value, and where it
crosses unity (dotted horizontal line) is the notional Einstein radius
$\Theta_{\text{E, sim}}$.  The two blue curves are the minimal and
maximal mean enclosed $\kappa$ from the internal ensemble in \spl.
The region between the blue curves is shaded between the radii of the
innermost and the outermost images --- this is the confidence region
from the modeling.  As we see, the shaded blue is slightly above the
red curve.  The Einstein Radius $\Theta_\text{E}$ of the model is
estimated crossing the mean enclosed $\kappa$ (not plotted) with
unity. \citep[see, e.g.,][]{2002LNP...608....1C}.

>>>>

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.8\linewidth]
             {fig/007025_kappa_encl}}
  \subfigure{\includegraphics[width=0.8\linewidth]
             {fig/007022_kappa_encl}}
  \subfigure{\includegraphics[width=0.8\linewidth]
             {fig/007021_kappa_encl}} \\
  \caption{Enclosed mass \kenc from three models of the same system.
    The upper panel corresponds to the model shown in \figref{7025},
    in which the minima and saddle-points have been incorrectly
    swapped.  The middle corresponds to \figref{7022}, where the image
    parities were correct.  The lower panel corresponds to another
    model, where the image parities were correct but the time-ordering
    was incorrect.  See text of Section~\ref{sec:example_models} for
    details.}
\label{fig:kapenc_compare_faulty}
\end{figure}

\figref{kapenc_compare_faulty} compares the circularly
averaged mass profiles for one input lens and three different models
of it.  Each panel shows the mean convergence $\kappa$ within a
circle of given radius, as a function of the radius.  The red curve is
the true value.  The two blue curves are the minimal and maximal mean
enclosed $\kappa$ from the internal ensemble in \spl.  Radial
locations of the images are marked, along with the image parities.
The region between the blue curves is shaded between the radii of the
innermost and the outermost images: this is the confidence region from
the modelling.

In a circular lens, the Einstein radius has averaged enclosed $\kappa$
of unity.  For a general, non-circular lens, there is no standard
definition of an Einstein radius.  We adopt a notional Einstein radius
$\Theta_E$ as the radius at which the mean enclosed $\kappa$ within a
circle is unity.  In \figref{kapenc_compare_faulty}, that would be
where the mean convergence crosses the dashed horizontal line.  Where
the red curve crosses $10^0$ is the actual Einstein radius
$\Theta_{E\rm,act}$.  The recovered Einstein radius
$\Theta_{E\rm,rec}$ and its uncertainty are given by the blue curves
crossing $10^0$.  We see that in all three panels, the blue curves are
shallower than the red curve and $\Theta_{E\rm,rec}$ is more than
$\Theta_{E\rm,act}$. by more than the model uncertainties.  Now,
steeper mass profiles tend to give wider image separations --- recall
that the image separation for a circular isothermal lens is
$2\Theta_E$, whereas for a point mass it is more \citep[see,
  e.g.,][]{2002LNP...608....1C} --- so $\Theta_{E\rm,rec}$ being too
high is really a consequence of the \spl models being too shallow for
the sims.
